Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Tweak control Fig

# -----------------------------------------------------------------------------------
results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(
    legend.position = c(1.4, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p14

@@

layout_matrix <- rbind(
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9),  
  c(3, 1, 1, 9, 9,  11, 11, 9), 
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)

>>>>

# -----------------------------------------------------------------------------------
results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p14

@@

layout_matrix <- rbind(
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(4, 2, 2, 5, 12, 10, 10, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9), 
  c(3, 1, 1, 5, 9,  11, 11, 9),  
  c(3, 1, 1, 9, 9,  11, 11, 9), 
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 13, 14, 14, 9),
  c(8, 6, 6, 9, 9,  15, 15, 9),
  c(8, 6, 6, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9),
  c(9, 9, 9, 9, 9,  15, 15, 9)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)
